Detecting AI-Generated Images using ResNet

### 2022-12-14 paper/paper.tex
Update paper

As shown in the table, on the validation set from the main dataset, the ResNet34 model has a higher accuracy, precision, recall and F1 score than the ResNet50 model. However, on the testing datasets, the ResNet50 model generally has a higher accuracy, precision, recall and F1 score than the ResNet34 model in most comparisons except for "Weather + DALLE2" dataset where ResNet50 is worse in F1 score. Even though the all the difference is within 10\%, this is a statistically significant trend that ResNet50 seems to generalize better on the dataset that it hasn't seen. This is likely due to the fact that the ResNet50 model has more layers than the ResNet34 model, which makes it more complex and has more parameters to learn. Thus, it can learn more features from the training dataset and generalize better to the testing datasets. However, the ResNet34 model is simpler and has less parameters to learn. Thus, it is more likely to overfit the training dataset and perform worse on the testing datasets.

>>>>

As shown in the table, on the validation split from the main dataset, the ResNet34 model has a higher accuracy, precision, recall and F1 score than the ResNet50 model. However, on the testing datasets, the ResNet50 model generally has a higher accuracy, precision, recall and F1 score than the ResNet34 model in most comparisons except for "Weather + DALLE2" dataset where ResNet50 is worse in F1 score. Even though the all the difference is within 10\%, this is a statistically significant trend that ResNet50 seems to generalize better on the dataset that it hasn't seen. This is likely due to the fact that the ResNet50 model has more layers than the ResNet34 model, which makes it more complex and has more parameters to learn. Thus, it can learn more features from the training dataset and generalize better to the testing datasets. However, the ResNet34 model is simpler and has less parameters to learn. Thus, it is more likely to overfit the training dataset and perform worse on the testing datasets.
